SVA-DEA benchmark

### 2020-08-04 main_figures/svadea.Rmd
simplified sva-dea figure

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(pipeComp)
  library(grid)
  library(ComplexHeatmap)
  library(circlize)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
res1 <- res <- readRDS("../svadea/results/aggregated.rds")
res1$evaluation$dea <- lapply(res1$evaluation$dea, FUN=function(x){
  x[which(x$k==1),]
})
```

@@

p <- plot_grid(
  plot_grid(
    dea_evalPlot_curve(res1, agg.by=c("sva.method","dea.method"), colourBy="dea.method", shapeBy="sva.method") + ggtitle("Using a single surrogate variable"),
    dea_evalPlot_curve(res, agg.by=c("sva.method","k"), colourBy="k", shapeBy="sva.method") + ggtitle("Increasing the number of surrogate variables"),
    nrow=2, labels=LETTERS[1:2]
  ),
  grid.grabExpr(draw( hts, heatmap_legend_side = "bottom", merge_legend=TRUE, 
                      annotation_legend_list=.scaledLegend())),
  nrow=1, rel_widths=c(5,2.2), labels=c(NA,"C")
)
pdf("svadea.pdf", width=11.5, height=6.8)
p
dev.off()
p
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(pipeComp)
  library(grid)
  library(ComplexHeatmap)
  library(circlize)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
res1 <- res <- readRDS("../svadea/results/aggregated.rds")
res1$evaluation$dea <- lapply(res1$evaluation$dea, FUN=function(x){
  x[which(x$k==1),]
})
res$evaluation$dea <- lapply(res$evaluation$dea, FUN=function(x){
  levels(x$k) <- c(levels(x$k), "0")
  x$k <- relevel(x$k, "0")
  x$k[x$sva.method=="none"] <- 0
  x
})
```

@@

res <- lapply(res$evaluation$dea, FUN=function(x){
  x[which(x$k %in% as.character(0:5)),]
})

cols <- c("#00204DFF", "#31446BFF", "#666970FF", "#958F78FF", "#CBBA69FF", "#FFEA46FF")
names(cols) <- 0:5

p <- plot_grid(
  plot_grid(
    dea_evalPlot_curve(res1, agg.by=c("sva.method"), colourBy="sva.method", shapeBy="sva.method") + ggtitle("Using a single surrogate variable"),
    dea_evalPlot_curve(res, agg.by=c("sva.method","k"), colourBy="k", shapeBy="sva.method") + 
      scale_colour_manual(values=cols) + ggtitle("Increasing the number of surrogate variables"),
    nrow=2, labels=LETTERS[1:2]
  ),
  grid.grabExpr(draw( hts, heatmap_legend_side = "bottom", merge_legend=TRUE, 
                      annotation_legend_list=.scaledLegend())),
  nrow=1, rel_widths=c(5,2.2), labels=c(NA,"C")
)
pdf("svadea.pdf", width=11.5, height=6.8)
p
dev.off()
p
```
